Development of a educational and sustainable robotic platform for children and adults

### 2013-11-13 doc/paper.tex
autocommited by makefile

The pin usage is similar to the pin usage of wheeled robots with two DC motors. The control is more difficult since the

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{images/omniwheel.jpg}
  \caption{Controm scheme of a omni wheel (from http://commons.wikimedia.org/wiki/File:Omni\_wheel\_control.jpg)}
\end{figure}

>>>>

The pin usage is similar to the pin usage of wheeled robots with two DC motors. The control is more difficult since the control scheme is complex due to the movement vectors.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{images/omniwheel.jpg}
  \caption{Control scheme of a omni wheel (from http://commons.wikimedia.org/wiki/File:Omni\_wheel\_control.jpg)}
\end{figure}
